Analysis of the included studies

### 2023-04-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Now sourcing the data cleaning script in the main analysis

```{r}
# Load the cleaned data 
long_data <- read_rds(file.path(data_dir, "review_data_long_cleaned.rds"))

>>>>

```{r}
#' re-run the data cleaning step, in case something has changed 
#' TO DO: Use GNU make for this

source("./orv_models_review_data_cleaning.R")

# Load the cleaned data 
long_data <- read_rds(file.path(data_dir, "review_data_long_cleaned.rds"))
